Universal Anonymous Signatures

### 2022-04-13 prism-backend/research/gsac/construction-uas.tex
Some refining of UAS generic construction.

% \subsubsection{Commitments}

% \todo{Introduce, and summarise correctness and security.}

% \begin{description}
%   \item[$\Cparm \gets \CSetup(\Csecpar).$]
%   \item[$(\Ccom,\Copn) \gets \CCommit(\Cparm,\msg).$] 
%   \item[$\Cproof \gets \CProve(\Ccom,\Copn,\msg).$]    
%   \item[$1/0 \gets \CVerify(\Cproof,\Ccom).$] 
% \end{description}

% \subsubsection{Signatures with Proofs of Knowledge}

% As put forward in \cite{cl02}, a generic way to build anonymous credentials
% requires a digital signature scheme with efficient protocols for proving
% knowledge of a digital signature, and signing committed values. This approach
% also has much in common with the Sign-Randomize-Prove (SRP) approach to build
% group signatures \needcite. Thus, even a priori, it seems a good core component
% to build something that is actually in betwween GS and AC. In the sequel, we use
% \RS to refer to schemes of this type, which must provide the functionality
% specified by the following syntax:

% \begin{description}
% \item[$(\RSvk,\RSsk) \gets \RSKeyGen(\RSsecpar,\RSlen)$.] Generates a key pair,
%   consisting on the signig key \RSsk and the verification key \RSvk, which
%   support sigining blocks of up to \RSlen messages.
% \item[$\RSsig \gets \RSSign(\RSsk,\msgset,\cmsgset)$.] Given signing key \RSsk,
%   a set of messages \msgset, and a set of commitments to messages, where
%   $|\msgset + \cmsgset| \le \RSlen$, returns a signature \RSsig.
% \item[$1/0 \gets \RSVerify(\RSvk,\RSsig,\amsgset)$.] Given a verification key
%   \RSvk, a signature \RSsig, supposedly over set of messages \amsgset which may
%   contain commitments to messages, returns $1$ or $0$. \todo{Assume that, within
%     \amsgset, it is possible to know which are commitments and wich plain
%     messages?}
% \item[$\RSproof/\bot \gets \RSProve(\RSsig,\amsgset,\D)$.] Given signature
%   \RSsig, over set of messages (and commitments to messages) \amsgset, out of
%   which those indexed by set \D are to be revealed, creates a proof of knowledge
%   \RSproof of \RSsig.
% \item[$1/0 \gets \RSProveVer(\RSproof,\msgset)$.] Given a proof of knowledge of
%   a signature over a set of messages, which includes \msgset, returns $1$ or
%   $0$.
% \end{description}

% \todo{Summarise correctness and security.}

% \subsubsection{Digital Signatures}

% \todo{Introduce, and summarise correctness and security.}

% \begin{description}
% \item[$(\Svk,\Ssk) \gets \SKeyGen(\Ssecpar)$.]
% \item[$\Ssig \gets \SSign(\Ssk,\msg)$.]
% \item[$1/0 \gets \SVerify(\Svk,\Ssig,\msg)$.]  
% \end{description}

% \subsubsection{Encryption}

% \todo{Introduce, and summarise correctness and security.}

% \begin{description}
% \item[$(\Eek,\Edk) \gets \EKeyGen(\Esecpar)$.]
% \item[$\Ec \gets \EEnc(\Eek,\msg)$.]
% \item[$\msg \gets \EDec(\Edk,\Ec)$.]
% \end{description}

% \subsubsection{Non-Interactive ZK Proofs of Knowledge}

% \todo{Introduce, and summarise correctness and security.}

% \begin{description}
% \item[$\NIZKcrs\gets \NIZKSetup(\NIZKsecpar)$.]
% \item[$\NIZKproof \gets \NIZKProve(\NIZKcrs,\NIZKx,\NIZKw)$.]
% \item[$1/0 \gets \NIZKVerify(\NIZKcrs,\NIZKproof,\NIZKx)$.]
% \end{description}

% We use $\NIZK^\Lang$ to denote a \NIZK which is used to prove statements on a
% given NP language \Lang.

% \subsubsection{Signature Proofs of Knowledge}

% \todo{Introduce, and summarise correctness and security.}

% \begin{description}
% \item[$\SPKproof \gets \SPKProve(\SPKmsg,\SPKx,\SPKw)$.]
% \item[$1/0 \gets \SPKVerify(\SPKproof,\SPKmsg,\NIZKx)$.]
% \end{description}

% We use $\SPK^\Lang$ to denote an \SPK which is used to prove statements on a
% given NP language \Lang.

@@

\paragraph{$\langle \cred/\bot,\utrans/\bot \rangle \gets
  \langle\Obtain(\usk,\scred,\attrs),\Issue(\isk,\upk,\scred,\attrs)\rangle$.} %
To obtain a new credential, a user with secret key usk and credentials $\cred_i$,
issued by issuers with public keys $\ipk_i$, requests a signature on commitments
of both the user key and a new random credential identifier -- similarly to
\GSAC. In addition, the user proves that the issuance function \fissue
established by the issuer is satisfied by the $\cred_i$ credentials and its user
secret key. For this, we define relation $\NIZKRel_{\Issue} = \lbrace (\usk,
\credid,\scred), (\Ccom,\attrs): \Ccom = \CCommit((\usk,\credid)) \land
\fissue(\usk,\scred,\attrs) = 1 \land \forall \cred \in \scred, \usk \in \cred
\rbrace$. \todo{Refine the notation for $\attr \in \cred$. Also, need to make
  the {\ipk}s explicit in it.} The interactive protocol from a user to obtain a
credential from an issuer of the system is as follows:

\begin{itemize}
\item \uline{User}: Compute a fresh credential identifier $\credid \getr
  \AttrSpace$, and commit to it along with the user secret key with
  $\Ccom \gets \CCommit((\usk,\credid))$. Compute proof $\NIZKproof \gets
  \NIZKProve^{\NIZKRel_{\Issue}}(\NIZKcrs_{\Issue},(\usk,\credid,\scred),
  (\Ccom,\attrs))$. Send $(\Ccom,\NIZKproof)$ to Issuer.
\item \uline{Issuer}: Verify \NIZKproof with $\NIZKVerify^{\NIZKRel_{\Issue}}
  (\NIZKcrs_{\Issue},(\Ccom,\attrs))$, and abort if it fails. Then, compute
  the credential by running $\cred \gets \SBCMSign(\SBCMsk,\Ccom,\attrs)$.
  Send \cred to User. Output $\utrans \gets (\Ccom,\attrs,\cred,\NIZKproof)$.
\item \uline{User}: Verify the credential with $\SBCMVerify(\SBCMvk,\cred,
  \attrs \cup \lbrace \usk,\credid \rbrace)$. Reject if verification fails.
  Otherwise, return \cred.
\end{itemize}

\paragraph{$(\sig,\yeval) \gets \Sign(\usk,\opk,\scred,\msg,\feval)$.} %
In the signing algorithm, we make use of the following relation:
$\NIZKRel_{\Sign} = \lbrace (\usk,\scred,\yinsp),(\msg,\feval,\yeval,\Ec,\sipk)
: \Ec = \EEnc(\Eek,\yinsp) \land \yeval = \feval(\usk,\scred,\msg) \land
\yinsp = \finsp(\yeval,\usk,\scred,\msg) \land \forall \cred \in \scred,
\SBCMVerify(\ipk,\cred,\attrs_{\cred} \cup \lbrace \usk,\credid \rbrace) = 1)
\rbrace$, where we make two syntax abuses, to ease readability: with
$\attrs_{\cred}$ we refer to the attributes in credential \cred, which its
legitimate owner can recover easily (e.g., from secure storage); and, as stated
before, $\ipk_{\cred}$ denotes the issuer public key of credential \cred, which
we also assume to be easily recoverable from \cred, by its legitimate owner.
\todo{Maybe, try to think of clearer naming conventions.}
%
From this, in order to produce a valid signature, the user first evaluates
$\yeval \gets \feval (\usk,\scred,\msg)$, and decides whether or not to continue
with the signing process -- this may depend, e.g., on the inspection policy of
\opk, as the output of \feval may influence whether the user will be
de-anonymizable or not, depending on the \finsp function in \opk.
%
Then, the user parses \opk as $(\Svk,\Eek,\finsp,\sig_{\finsp})$ and checks that
$\Verify(\Svk,\sig_{\finsp},\finsp) = 1$ (note that this step may be cached), to
compute $\yinsp \gets \finsp(\yeval,\usk,\scred,\msg)$, and encrypt it with
\Eek by running $\Ec \gets \EEnc(\Eek,\yeval)$. Finally, the user computes
$\NIZKproof \gets \NIZKProve^{\NIZKRel_{\Sign}}(\NIZKcrs_{\Sign},(\usk,\scred,
\yinsp))$ and  outputs $(\sig = (\NIZKproof,\Ec),\yeval)$.

>>>>

@@

\paragraph{$\langle \cred/\bot,\utrans/\bot \rangle \gets
  \langle\Obtain(\usk,\scred,\attrs),\Issue(\isk,\upk,\scred,\attrs)\rangle$.} %
To obtain a new credential, a user with secret key usk and credentials $\cred_i$,
issued by issuers with public keys $\ipk_i$, requests a signature on commitments
of both the user key and a new random credential identifier -- similarly to
\GSAC. In addition, the user proves that the issuance function \fissue
established by the issuer is satisfied by the $\cred_i$ credentials and its user
secret key. For this, we define relation $\NIZKRel_{\Issue} = \lbrace (\usk,
\scred), (\Ccom,\attrs): \Ccom = \CCommit(usk) \land \fissue(\usk,\scred,
\attrs) = 1 \land \forall \cred \in \scred, \SBCMVerify(\ipk_{\cred},\cred,
\attrs_{\cred} \cup \lbrace \usk \rbrace) = 1 \rbrace$. The interactive protocol
for a user to obtain a credential from an issuer of the system is as follows:

\begin{itemize}
\item \uline{User}: Commit to the user secret key with $\Ccom \gets
  \CCommit(\usk)$. Compute proof $\NIZKproof \gets
  \NIZKProve^{\NIZKRel_{\Issue}}(\NIZKcrs_{\Issue},(\usk,\scred),(\Ccom,
  \attrs))$. Send $(\Ccom,\NIZKproof)$ to Issuer.
\item \uline{Issuer}: Verify \NIZKproof with $\NIZKVerify^{\NIZKRel_{\Issue}}
  (\NIZKcrs_{\Issue},(\Ccom,\attrs))$, and abort if it fails. Then, compute
  the credential by running $\cred \gets \SBCMSign(\SBCMsk,\Ccom,\attrs)$.
  Send \cred to User. Output $\utrans \gets (\Ccom,\attrs,\cred,\NIZKproof)$.
\item \uline{User}: Verify the credential with $\SBCMVerify(\SBCMvk,\cred,
  \attrs \cup \lbrace \usk \rbrace)$. Reject if verification fails.
  Otherwise, return \cred.
\end{itemize}

\paragraph{$(\sig,\yeval) \gets \Sign(\usk,\opk,\scred,\msg,\feval)$.} %
In the signing algorithm, we make use of the following relation:
$\NIZKRel_{\Sign} = \lbrace (\usk,\scred,\yinsp),(\msg,\feval,\yeval,\Ec,\sipk)
: \Ec = \EEnc(\Eek,\yinsp) \land \yeval = \feval(\usk,\scred,\msg) \land
\yinsp = \finsp(\yeval,\usk,\scred,\msg) \land \forall \cred \in \scred,
\SBCMVerify(\ipk_{\cred},\cred,\attrs_{\cred} \cup \lbrace \usk \rbrace) = 1)
\rbrace$, where we make two syntax abuses, to ease readability: with
$\attrs_{\cred}$ we refer to the attributes in credential \cred, which its
legitimate owner can recover easily (e.g., from secure storage); and, as stated
before, $\ipk_{\cred}$ denotes the issuer public key of credential \cred, which
we also assume to be easily recoverable from \cred, by its legitimate owner.
\todo{Maybe, try to think of clearer naming conventions.}
%
From this, in order to produce a valid signature, the user first evaluates
$\yeval \gets \feval (\usk,\scred,\msg)$, and decides whether or not to continue
with the signing process -- this may depend, e.g., on the inspection policy of
\opk, as the output of \feval may influence whether the user will be
de-anonymizable or not, depending on the \finsp function in \opk.
%
Then, the user parses \opk as $(\Svk,\Eek,\finsp,\sig_{\finsp})$ and checks that
$\Verify(\Svk,\sig_{\finsp},\finsp) = 1$ (note that this step may be cached), to
compute $\yinsp \gets \finsp(\yeval,\usk,\scred,\msg)$, and encrypt it with
\Eek by running $\Ec \gets \EEnc(\Eek,\yeval)$. Finally, the user computes
$\NIZKproof \gets \NIZKProve^{\NIZKRel_{\Sign}}(\NIZKcrs_{\Sign},(\usk,\scred,
\yinsp))$ and  outputs $(\sig = (\NIZKproof,\Ec),\yeval)$.

### 2022-04-13 prism-backend/research/gsac/model-uas.tex
Some refining of UAS generic construction.

\begin{description}
\item[$\parm \gets \Setup(\secpar)$.] Given a security parameter \secpar,
  returns a global system parameter variable \parm.
\item[$(\ipk,\isk) \gets \IKeyGen(\parm,\fissue)$.] Given global system
  parameters \parm, and the function \fissue to be used to check that credential
  requestors meet the conditions to be issued a credential, an issuer runs
  \IKeyGen to generate its issuing key pair. 
\item[$(\opk,\osk) \gets \OKeyGen(\parm,\finsp)$.] Given global system
  parameters \parm, and function \finsp, an inspector runs \OKeyGen to generate
  its inspecting key pair. The function \finsp defines the type of utility that
  will be extractable from those pairs that do not meet conditions defined
  at signing time (typically, by verifiers).
\item[$\usk \gets \UKeyGen(\parm)$.] Given global system parameters
  \parm, returns a user's secret key.
\item[$\langle \cred/\bot,\utrans/\bot \rangle \gets
  \langle
  \Obtain(\usk,\lbrace (\cred_i,\ipk_i)\rbrace_{i \in \Issuers},\attrs),
  \Issue(\isk,\lbrace \ipk_i \rbrace_{i \in \Issuers},\attrs))
  \rangle$.] %
  This interactive protocol lets a user with key \usk running the
  \Obtain process, receive a credential \cred from an issuer in the system, on
  attribute set $\attrs$. The user leverages a set of $(\cred_i,\ipk_i)$ pairs,
  where $\cred_i$ is a credential obtained from the issuer with public
  key $\ipk_i$. The user outputs the produced credential \cred, while
  the issuer outputs the protocol transcript \utrans for the produced
  credential. To ease notation, we assume that the group to which each
  credential belongs is available from the credential itself, and therefore
  omit the $\ipk_i$ values from the syntax, unless necessary to avoid ambiguity.
\item[$(\sig,\yeval) \gets \Sign(\usk,\opk,\lbrace (\cred_i,\ipk_i)
  \rbrace_{i \in \Issuers},\msg,\feval)$.] %
  Upon receiving a user secret key \usk, inspector public key \opk, a set of
  credential-issuer pairs $(\cred_i,\ipk_i)$, a message \msg and evaluation
  function \feval, returns signature \sig and value \yeval.
\item[$1/0 \gets \Verify(\opk, \lbrace \ipk_i \rbrace_{i \in \Issuers},\sig,
  \yeval,\msg,\feval)$.] Checks whether $(\sig,\yeval)$ is a valid signature
  over message \msg, from a user with credentials issued by issuers with public
  keys $\ipk_i$, for evaluation function \feval and inspector key \opk.
\item[$(\yinsp,\iproof)/\bot \gets \Inspect(\osk,\lbrace \ipk_i
  \rbrace_{i \in \Issuers},\sig,\yeval,\msg,\feval)$.] %
  \todo{I think we do not need \trans here, see the generic construction. (This
    was somehow inherited from \cite{bsz05}.) However, if it is indeed not
    needed, it is noteworthy that we include/need it in \GSAC, but not here.
    Justify/understand better why!}
  Executed by the inspector with private key \osk. Receives a signature $(\sig,
  \yeval)$ over message \msg and evaluation function \feval, generated using
  credentials issued by the issuers with public keys $\ipk_i$. If \sig is valid,
  the function outputs a value $\yinsp$ derived from the signer's public key,
  credentials, message, and signature, as well as a proof of correct
  inspection.
\item[$1/0 \gets \Judge(\opk,\lbrace ipk_i \rbrace_{i \in \Issuers},\yinsp,
  \iproof,\sig,\yeval,\msg,\feval)$.] %
  Checks if \iproof is a valid inspection correctness proof for the value \yinsp,
  obtained by applying \Inspect to the the signature $(\sig,\yeval)$ over
  message \msg, and for evaluation function \feval. 
\end{description}

>>>>

\begin{description}
\item[$\parm \gets \Setup(\secpar)$.] Given a security parameter \secpar,
  returns a global system parameter variable \parm.
\item[$(\ipk,\isk) \gets \IKeyGen(\parm,\fissue)$.] Given global system
  parameters \parm, and the function \fissue to be used to check that credential
  requestors meet the conditions to be issued a credential, an issuer runs
  \IKeyGen to generate its issuing key pair. 
\item[$(\opk,\osk) \gets \OKeyGen(\parm,\finsp)$.] Given global system
  parameters \parm, and function \finsp, an inspector runs \OKeyGen to generate
  its inspecting key pair. The function \finsp defines the type of utility that
  will be extractable from those pairs that do not meet conditions defined
  at signing time (typically, by verifiers).
\item[$\usk \gets \UKeyGen(\parm)$.] Given global system parameters
  \parm, returns a user's secret key.
\item[$\langle \cred/\bot,\utrans/\bot \rangle \gets
  \langle
  \Obtain(\usk,\lbrace (\cred_i,\ipk_i)\rbrace_{i \in \Issuers},\attrs),
  \Issue(\isk,\lbrace \ipk_i \rbrace_{i \in \Issuers},\attrs))
  \rangle$.] %
  This interactive protocol lets a user with key \usk running the
  \Obtain process, receive a credential \cred from an issuer in the system, on
  attribute set $\attrs$. The user leverages a set of $(\cred_i,\ipk_i)$ pairs,
  where $\cred_i$ is a credential obtained from the issuer with public
  key $\ipk_i$. The user outputs the produced credential \cred, while
  the issuer outputs the protocol transcript \utrans for the produced
  credential. To ease notation, we assume that the group to which each
  credential belongs is available from the credential itself, and therefore
  omit the $\ipk_i$ values from the syntax, unless necessary to avoid ambiguity.
\item[$(\sig,\yeval) \gets \Sign(\usk,\opk,\lbrace (\cred_i,\ipk_i)
  \rbrace_{i \in \Issuers},\msg,\feval)$.] %
  Upon receiving a user secret key \usk, inspector public key \opk, a set of
  credential-issuer pairs $(\cred_i,\ipk_i)$, a message \msg and evaluation
  function \feval, returns signature \sig and value \yeval.
\item[$1/0 \gets \Verify(\opk, \lbrace \ipk_i \rbrace_{i \in \Issuers},\sig,
  \yeval,\msg,\feval)$.] Checks whether $(\sig,\yeval)$ is a valid signature
  over message \msg, from a user with credentials issued by issuers with public
  keys $\ipk_i$, for evaluation function \feval and inspector key \opk.
\item[$(\yinsp,\iproof)/\bot \gets \Inspect(\osk,\lbrace \ipk_i
  \rbrace_{i \in \Issuers},\sig,\yeval,\msg,\feval)$.] %
  Executed by the inspector with private key \osk. Receives a signature $(\sig,
  \yeval)$ over message \msg and evaluation function \feval, generated using
  credentials issued by the issuers with public keys $\ipk_i$. If \sig is valid,
  the function outputs a value $\yinsp$ derived from the signer's public key,
  credentials, message, and signature, as well as a proof of correct
  inspection.
\item[$1/0 \gets \Judge(\opk,\lbrace ipk_i \rbrace_{i \in \Issuers},\yinsp,
  \iproof,\sig,\yeval,\msg,\feval)$.] %
  Checks if \iproof is a valid inspection correctness proof for the value \yinsp,
  obtained by applying \Inspect to the the signature $(\sig,\yeval)$ over
  message \msg, and for evaluation function \feval. 
\end{description}
